Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2015-06-22 paper/letter.tex
update
removed subtitles
paragraph on total M_HI mass

@@

@@

@@

6. Comparison of these results against other observational data.

>>>>

%\section{Introduction}

@@

%\section{TOL1214-277}

@@

TOL1214-277 Blue Compact Dwarf Galaxy

Star forming galaxy, no old stars.

%\section{Results}

@@

%6. Comparison of these results against other observational data.

We estimate the total neutral hydrogen mass to be $M\approx
m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
the optical depth and $n$ is the number density of neutral Hydrogen
atoms. For this system we estimate that for average values of
$n=1\times 10^3$ the total hydrogen mass is $M\times
10^{14}$M$_{\odot}$. However, blind HI surveys have put an upper limit
in the neutral hydrogen mass of ???
